A comparison of design-based and model-based approaches for spatial data.

### 2021-08-11 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd
minor updates

@@

# mike chunk
# combo_data <- purrr::map_df(files,
#                             ~read_csv(.x) %>% mutate(filename = .x)) %>%
#   separate(filename, into = c("junk", "junk2", "error_dep", "dist", "n", "location"),
#            sep = "_") %>%
#   select(-junk, -junk2)

# matt chunk
combo_data <- purrr::map_df(files,
                            ~read_csv(.x) %>% mutate(filename = .x)) %>%
  separate(filename, into = c("junk", "error_dep", "dist", "n", "location"),
           sep = "_") %>%
  select(-junk)

>>>>

There were several variables to alter in the simulations, and the names of the scenarios in future plots mirror these variables

* correlation type: dependent errors or independent errors
* error type:
    * normal: mean 0, variance 2
    * lognormal: log scale mean 0, log scale variance 2
    * lognormalbig: log scale mean 0, log scale variance 4
* sample sizes: $n = 10, 50, 150; N = 900$
* layout: gridded vs random population locations

So for example, the `inderror.normal.n50.randloc` is the simulation having independent random errors that are normal, a sample size of 50, and random population locations.

In each simulation, a GRTS sample and an IRS sample were selected. Then for the GRTS sample, the design-based approach using the local neighborhood variance (Design GRTS) and a model-based approach were applied (Model GRTS). Then for the IRS sample, the design-based approach using the simple random sample variance (Design IRS) and a model-based approach were applied (Model IRS).

@@

# mike chunk
combo_data <- purrr::map_df(files,
                            ~read_csv(.x) %>% mutate(filename = .x)) %>%
  separate(filename, into = c("junk", "junk2", "error_dep", "dist", "n", "location"),
           sep = "_") %>%
  select(-junk, -junk2)

# matt chunk
# combo_data <- purrr::map_df(files,
#                             ~read_csv(.x) %>% mutate(filename = .x)) %>%
#   separate(filename, into = c("junk", "error_dep", "dist", "n", "location"),
#            sep = "_") %>%
#   select(-junk)

### 2021-08-11 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.tex
minor updates

>>>>

There were several variables to alter in the simulations, and the names
of the scenarios in future plots mirror these variables

\begin{itemize}
\tightlist
\item
  correlation type: dependent errors or independent errors
\item
  error type:

  \begin{itemize}
  \tightlist
  \item
    normal: mean 0, variance 2
  \item
    lognormal: log scale mean 0, log scale variance 2
  \item
    lognormalbig: log scale mean 0, log scale variance 4
  \end{itemize}
\item
  sample sizes: \(n = 10, 50, 150; N = 900\)
\item
  layout: gridded vs random population locations
\end{itemize}

So for example, the \texttt{inderror.normal.n50.randloc} is the
simulation having independent random errors that are normal, a sample
size of 50, and random population locations.

In each simulation, a GRTS sample and an IRS sample were selected. Then
for the GRTS sample, the design-based approach using the local
neighborhood variance (Design GRTS) and a model-based approach were
applied (Model GRTS). Then for the IRS sample, the design-based approach
using the simple random sample variance (Design IRS) and a model-based
approach were applied (Model IRS).
